Feature importance analysis

### 2020-03-17 analysis/feature-importance.Rmd
workflowr::wflow_publish("analysis/feature-importance.Rmd")

library("drake")
library("hsdar")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("ggpmisc")
library("patchwork")

@@

@@

>>>>

library("drake")
library("hsdar")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("ggpmisc")
library("patchwork")
library("iml")

@@

  fi_ale_hr_buffer2,

@@

# ALE plots

ALE plots via package {iml}

```{r}
fi_ale_hr_buffer2$plot(ncols = 2)
```
